---
title: "Investigate Assignment 1 - Ogozaly"
author: "Walter Ogozaly"
date: "11/2/2020"
output:
  pdf_document: default
  html_document: default
---

In an ANOVA analysis of Kila loan amounts issued in Mexico, India, and Indonesia, results showed evidence that at least one of the countries' mean loan amount differed significantly from the rest. 

The parameters for the analysis were:

mu1 = population 'Mexico' mean

mu2 = country 'Indonesia' mean

mu3 = country 'India' mean

———

Our hypotheses were:

$$H_{o}:  μ_{1} = μ_{2} = μ_{3}$$

$$H_{a}: Some\  μ_{i} =/= μ_{j}$$

This analysis assumes that the effects are constant and additive. It also assumes that the residuals are random, independent, and normally distributed. Residuals are assumed to have the same variability in each group. 

The test statistic in the analysis is 234.63, indicating that the difference between populations greatly exceeds the expected amount of error. The p-value is 2.2e-16, indicating that the probability of obtaining this result if our null hypothesis were true is exceedingly low.

A possible limitation to this analysis is that the data is not quite normally distributed. One tail is much thicker than the other due to the presence of several high outlier loan amounts.

In conclusion, with a very small p-value, we have evidence that at least one of the population mean Kila loan amounts for the three countries is different from the rest. Our test statistic is also much larger than 1 . All evidence indicates that the null hypothesis is not true


We'll start by loading the necessary libraries.
```{r, message=FALSE}
library("tidyverse")
library("readxl")
```

Now we load the file and filter for Mexico, India, and Indonesia. 
```{r, message=FALSE, warning=FALSE}


kiva_sample <- read_excel("C:/Users/walte/OneDrive/Documents/RStudio Working Directory/Kiva_Sample.xlsx")


kiva_for_my_three_countries <- filter(kiva_sample, country =="India" | country == "Mexico" | country == "Indonesia")
```

Below is a box plot showing loan amounts by country. Mexico has the largest Kiva loan amounts, followed by Indonesia and finally India. 

Outliers have been excluded for visual clarity. All three countries have outliers in the direction of larger loans. Mexico has the highest outliers, as one might expect. Sample sizes are large enough, however, that we can proceed with the ANOVA test.

```{r boxplot}

boxplot(loan_amount~country,data=kiva_for_my_three_countries,outline=FALSE, col=(c("orange","red","darkgreen")))
```



Finally we'll run the ANOVA analysis. The test statistic is 234.63 and the p-value is 2.2e-16. 

```{r}

kiva_anova <- aov(kiva_for_my_three_countries$loan_amount~kiva_for_my_three_countries$country)

anova(kiva_anova)

```


